\section{Domain Platforms Evaluation}
\label{sec:EvaOp}

To set the stage for our proposed domain DSE approach \newtext{(DSS and \ga)},
this sections introduces our assumptions / formalization about the
target platform in~\secref{sec:Platform}, \newtext{and different evaluation options of domain platform, Analytic Evaluation (AE)} in~\secref{sec:Ana} and Domain Score (DS) in~\secref{sec:ds}. ~\secref{sec:eva:sum} \newtext{discusses the accuracy and speed trade-off of these evaluation options.}

\input{tex/EvalPlatform.tex}
\input{tex/EvalAna.tex}
\input{tex/EvalDS.tex}


\subsection{Trade-off: Evaluation Speed / Accuracy }
\label{sec:eva:sum}

To compare the the evaluation approaches in terms of accuracy and speed, we analyze them for a set of 40 real vision applications on 100 different platforms (with the same HW budget=5) against execution on a cycle-approximate TLM. % please name the few
\tabref{tab:fidelity} illustrates the trade-off looking at fidelity instead of accuracy as the evaluation approaches are compare design alternatives. TLM is defined as 100\% fidelity for this comparison.

\begin{table}[h]
	\caption{Fidelity and Speed: DS, \newtext{AE}, TLM}
	\label{tab:fidelity}
	\centering
	%\vspace{-10pt}
	\begin{tabular}{r||c|c|c}
		\toprule
		  & \textbf{DS}& \textbf{AE}& \textbf{TLM}\\
		\hline
		\midrule
		\textbf{Fidelity} & 89.07\%& 95.68\%& 100\%\\
		\hline
		\textbf{Eval. App [s]} & $7.2*10^{-5}$ & $6.0*10^{-4}$ & $1.8*10^2$ \\
		\hline
		\textbf{Eval. Domain [s]} & $7.2*10^{-5}$ & $6.0*10^{-2}$ & $1.8*10^4$ \\
		\bottomrule
	\end{tabular}
\end{table} 

Fidelity drops with abstraction: AE with 95.68\% and DS with 89.07\%. At the same time, abstraction yields dramatic speedups of 6 orders of magnitude from TLM to AE and another order of magnitude to DS. When evaluating a whole domain, DS is even 3 orders of magnitude faster than AE (assuming 100 apps in the domain) due to inherently incorporating all applications. In result, DS is preferred for rapid analysis, whereas the AE if more accuracy is needed. TLM simulation is too slow for DS-DSE.